acquisition of TEs

### 2021-05-18 Analyze_TEs.Rmd
fixed typos

simulation3 <- function (V) {
  D_seq = seq(100, V, by = 100) # sequence of D from 100 to V at an interval of 50
  N_seq = seq(0, V, by = 25) # sequence of N from 0 to V at an interval of 25
  D <- rep(D_seq, length(N_seq))
  N <- rep(N_seq, length(D_seq))
  data_simulation3 <<- data.frame(V, D, N)
}

@@

plot(keepers_ws_TE$balance_vocab, keepers_ws_TE$LangNonDom_input,
     xlab = "Vocabulary balance (= N/W)",
     ylab = "raw exposure to the non-dominant language") +
  lines(lowess(keepers_ws_TE$balance_vocab, keepers_ws_TE$LangNonDom_input), col="blue") # lowess line (x,y)

  abline(lm(keepers_ws_TE$LangNonDom_input~keepers_ws_TE$balance_vocab), col="red") # regression line (y~x)
lines(lowess(wt,mpg), col="blue") # lowess line (x,y)

>>>>

simulation3 <- function (V) {
  D_seq = seq(100, V, by = 100) # sequence of D from 100 to V at an interval of 100
  N_seq = seq(0, V, by = 25) # sequence of N from 0 to V at an interval of 25
  D <- rep(D_seq, length(N_seq))
  N <- rep(N_seq, length(D_seq))
  data_simulation3 <<- data.frame(V, D, N)
}

@@

     xlab = "Vocabulary balance (= N/W)",
balance_correlation <- plot(keepers_ws_TE$balance_vocab, keepers_ws_TE$LangNonDom_input,
                            xlab = "Vocabulary balance (= N/W)",
                            ylab = "Raw exposure to the non-dominant language",
                            cex.lab=1.0) +
  #lines(lowess(keepers_ws_TE$balance_vocab, keepers_ws_TE$LangNonDom_input), col="blue") # lowess line (x,y)
  abline(lm(keepers_ws_TE$LangNonDom_input~keepers_ws_TE$balance_vocab), col="red") # regression line (y~x)
